---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nbadownloader

<!-- badges: start -->
<!-- badges: end -->

This R package, nbadownloader, is a utility package that helps you download nba data from stat.nba.com easily. 

## Installation

There's no version of nbadownloader on CRAN. You can install the development version from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("GymRat102/nbadownloader")
```
## Example

This is a basic example which shows you how to fetch Luka Doncic's shot data in 2019-20 season and return a dataframe in your R environment:

``` r
library(nbadownloader)

## 1629029 is Luka's playerId, which you need to look up on stat.nba.com by your own at this stage.
Luka_shotdata_201920 <- get_shotdata("2019-20", "1629029") 
```

The returned dataframe is like this:

```{r}
library(dplyr)
glimpse(Luka_shotdata_201920)
```

The dataframe includes tons of information about every shot, especially x, y coordinates. For example, you can draw a super simple shot chart with the help of ggplot2:

```{r}
Luka_shotdata_201920$LOC_X <- as.numeric(as.character(Luka_shotdata_201920$LOC_X))
Luka_shotdata_201920$LOC_Y <- as.numeric(as.character(Luka_shotdata_201920$LOC_Y))

Luka_shotdata_201920 %>% 
  ggplot(aes(x = LOC_X, y = LOC_Y)) + 
  geom_point() +
  coord_equal()
```

